Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful?

### 2015-03-11 dm101.tex
Updates from ShareLaTeX

Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
the wrong functionality. For a very long list of software-related errors,
see  Peter Neumann's ``Risk Digest''\footnote{http://catless.ncl.ac.uk/Risks/}.

Because of the above, is important to thoroughly {\em test} software before it is {\em used}.
Such testing  can be very expensive.
Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
Lowry et al. warn that  
the state space explosion problem imposes
strict limits on how much a system can be explored
via automatic formal methods~\cite{lowrey98}.
For standard black-box testing methods,
a {\em linear} increase
in the confidence $C$ that we have found all defects
can take {\em exponentially} more effort.
For example, for one-in-a-thousand detects,
moving $C$ from  
90\% to 98\% nearly doubles the number of required tests (2301 to   3910 black box
probes, respectively)\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=\frac{log(1 -
C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}.

@@

{\em Widely used:} Many researchers use static attributes to guide software 
quality predictions.
Verification and validation (V\&V) textbooks
(\cite{rakitin01}) advise using static code complexity attributes
to decide which modules are worthy of manual inspections.  
For several  years, one of us (Menzies) worked on-site at the NASA software Independent Verification
and Validation facility
and he
knows of several large government software contractors that won't
review software modules {\em unless} tools like McCabe predict that
they are fault prone.

{\em Useful:}
A
standard result for defect predictors is that they find the location of  70\% (or more)
of the defects in code~\cite{me70b}.
Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey). When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.
A subsequent study on the Turkish software
compared how much code needs to be inspected using
random selection vs. selection via defect
predictors. Using random testing, 87\% of the files
would have to be inspected in order to detect 87\%
of the defects. However, if the inspection process
was restricted to the 25\% of the files that trigger
the defect predictors, then 88\% of the defects
could be found. That is, the same level of defect
detection (after inspection) can be achieved using
$(87-25)/87=71$\%less effort
\cite{tosun09}.

This is markedly
higher than other currently-used
industrial
methods such as manual code reviews. For example, 
A panel at {\em IEEE Metrics
2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
of defects.
In other work, 
Raffo found that the defect detection capability of
industrial review methods have mode defect detection rates
of around 50\%
 for full Fagan inspections~\cite{fagan76} to
21\% for less-structured inspections.

@@

>>>>

Human programmers are clever, but flawed. Coding  adds functionality, but also defects.
Hence, software sometimes crashes (perhaps at the most awkward or dangerous moment) or delivers
the wrong functionality. For a very long list of software-related errors,
see  Peter Neumann's ``Risk Digest'' at catless.ncl.ac.uk/Risks.

Since programming inherently
introduces defects into  programs, is important to thoroughly {\em test} software before it is {\em used}.
Such testing  can be very expensive.
Software assessment budgets are finite
while assessment effectiveness increases 
exponentially with assessment effort.
Lowry et al. warn that  
the state space explosion problem imposes
strict limits on how much a system can be explored
via automatic formal methods~\cite{lowrey98}.
For standard black-box testing methods,
a {\em linear} increase
in the confidence $C$ that we have found all defects
can take {\em exponentially} more effort.
For example, for one-in-a-thousand detects,
moving $C$ from  
90\% to 98\% nearly doubles the number of required tests (2301 to   3910 black box
probes, respectively)\footnote{A randomly selected 
input to a program will find a fault with probability $p$.
After $N$ random black-box tests, the chances of the inputs 
not revealing any fault 
is $(1-p)^N$. Hence, the chances $C$ of seeing the fault is $1-(1-p)^N$
which can be rearranged to 
 $N(C,p)=\frac{log(1 -
C)}{log(1-p)}$. For example, $N(0.90,10^{-3})=2301$.}.

@@

{\em Widely used:} Many researchers and industrial practitioners  use static attributes to guide software 
quality predictions.
 Defect prediction models have been reported
to have been used at Google~\cite{lewis13}.
Verification and validation (V\&V) textbooks
(\cite{rakitin01}) advise using static code complexity attributes
to decide which modules are worthy of manual inspections.  
For several  years, one of us (Menzies) worked on-site at the NASA software Independent Verification
and Validation facility
and he
knows of several large government software contractors that won't
review software modules {\em unless} tools like McCabe predict that
they are fault prone.

{\em Useful:}
A
standard result for defect predictors is that they find the location of  70\% (or more)
of the defects in code~\cite{me07b}.
Defect predictors developed at NASA~\cite{me07b} have also been used in software development companies outside the US (in Turkey). When the inspection teams focused on the modules that trigger the defect predictors, they found up to 70\% of the defects using just 40\% of their QA effort (measured in staff hours)~\cite{tosun10}.
A subsequent study on the Turkish software
compared how much code needs to be inspected using
random selection vs. selection via defect
predictors. Using random testing, 87\% of the files
would have to be inspected in order to detect 87\%
of the defects. Further, if the inspection process
was restricted to the 25\% of the files that trigger
the defect predictors, then 88\% of the defects
could be found. That is, the same level of defect
detection (after inspection) can be achieved using
$(87-25)/87=71$\%less effort
\cite{tosun09}.

@@

The success of this method in  predictors in finding bugs is   markedly
higher than other currently-used
industrial
methods such as manual code reviews. For example, 
a  panel at {\em IEEE Metrics
2002}~\cite{shu02} concluded that manual software  reviews can find ${\approx}60\%$ 
of defects.
In other work, 
Raffo documents the typical    defect detection capability of
industrial review methods:   around 50\%
 for full Fagan inspections~\cite{fagan76} to
21\% for less-structured inspections.

Note only do static code defect predictors perform well compared to manual methods,
they also are competititve with certain automatic methods.
At ICSE'14, Rahman et al.~\cite{rahman14:icse} offered an extensive comparison of:
\bi
\item The static code analysis tools FindBugs, Jlint, and Pmd;
\item Against static code defect predictors
(which they called ``statistical defect prediction'') build using logistic regression.
\ei
That study assessed the cost-effectiveness of finding bugs using either method.
They found   no significant differences in the cost-effectiveness
of the two approaches. Given this equivalence, it is significant to note that 
static code defect prediction can be quickly adapted to new languages, just by building lightweight
parsers that can extract information like \fig{ck}. The same cannot be said for   static code analyzers that require extensive modification before they can be applied to a new
language.
